RJObject Paper

### 2014-06-14 Documents/Paper/ms.tex
Starfield reference
Words about sinusoid

\section{Sinusoidal Example}
Phase transition

@@

\begin{thebibliography}{}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011b}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

>>>>

\section{Sinusoidal Example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different frequencies and amplitudes.
This kind of model has many applications\citep[see e.g.][]{bretthorst}.

@@

\begin{thebibliography}{}

\bibitem[Brewer et al.(2013)]{2013AJ....146....7B} Brewer, B.~J., 
Foreman-Mackey, D., Hogg, D.~W.\ 2013.\ Probabilistic Catalogs for Crowded 
Stellar Fields.\ The Astronomical Journal 146, 7.

\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011b}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
